\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{url}
\usepackage{graphicx}
\graphicspath{ {./images/} }

\pagenumbering{arabic}

\title{Installing XPDP1: Windows Subsystem for Linux (WSL) Edition}
\author{}
\date{Last updated: August 2018}

\begin{document}
	\maketitle

	\section{Installing WSL}

	\noindent Since WSL is still considered ``beta" software and thus changes frequently, any installation guide will be also changing frequently. To make things easier and more up-to-date until the platform stabilizes further, Microsoft's installation guide is the best to use here. It can be found at \url{https://docs.microsoft.com/en-us/windows/wsl/install-win10}. \\
	
	\noindent For any issues encountered while installing WSL, please refer to the Troubleshooting section in the above guide. 

	\section{Installing XPDP1}

	\noindent Now that WSL is installed and configured on your machine, please proceed with the ``Installing XPDP1: Linux Edition" guide. \\

	\noindent After completing this, XPDP1 should be installed and configured! To read the full XPDP1 documentation, see the file \verb|xpdp1_manual.ps| file inside of the \verb|doc| directory, which can be opened natively in Ubuntu. To create this file in another format (like PDF) run the \verb|xpdp1_manual.tex| file in a compatible PDF\LaTeX \hspace{1pt} compiler. To see a quick rundown of how to use the XPDP1 command at any time, simply type \verb|xpdp1 --help| in any Terminal command prompt.
\end{document}
